ext_risk_copula

### 2019-02-20 ext_risk_copula.Rmd
omitting acf results; adding r upto bifurcation points : 95% interval

#Ricker model :
```{r sim_ricker, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")
rlist<-c(0,0.1,0.3,0.5,0.7,0.9,1.0,1.1,1.3,1.5,1.7,1.9) #rc = 1
numsims<-10000
numsteps<-25
numlocs<-5
K<-50
scl<-1
ext_thrs<-K/10
model<-"ricker"

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

```{r fig_ricker, echo=F, results="hide",cache=T, cache.extra=list(seed,res_ricker_local,res_ricker_global)}
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()

pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, pch=16, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()
```

@@

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = c(0,2),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=1,lty="dotted") #rc=1

@@

rlist<-seq(from=1.5,to=7.5,by=0.5)
numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
scl<-1
rc_hassell<-((b/(b-1)))^b # critical value of r from monotonic to osc steady state approach transition 
rlist<-sort(c(rlist,rc_hassell))

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

# For global dispersion
res_hassell_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

```{r fig_hassell, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=9,width=18)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,6.2))

@@

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=9,width=18)
op<-par(mfrow=c(3,5),mar=c(5.2,4.2,1.2,6.2))

@@

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()
```

@@

rc_msmith<-b/(b-1)
rlist<-sort(c(seq(from=1.2,to=2.8,by=0.2),rc_msmith))

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

# For global dispersal in D matrix 
res_msmith_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

```{r fig_msmith, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()

pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

```{r get_rc_pennycuick,echo=F,results="hide",cache=T,cache.extra=list(seed,mtime("1var_pop_model_bifurcation.R"))}
source("./1var_pop_model_bifurcation.R")
a_pennycuick<-0.1
b_pennycuick<-0.1
eps<-1e-10 #you can change it upto which decimal point you want it to be exact
rlist<-seq(from=4.3231657,to=4.3231658,by=eps)
res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r,a,b),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}

@@

rc_pennycuick<-rlist[which.min(abs(res_pennycuick-0))]
formatC(rc_pennycuick,digits = 10, format="f") # accurate upto 10th decimal
```

```{r sim_pennycuick, echo=F,  results="hide", cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

rlist<-sort(c(seq(from=2,to=7,by=0.5),rc_pennycuick))

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

# For global dispersal in D matrix 
res_pennycuick_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

```{r fig_pennycuick, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=15)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

rlist<-seq(from=0.2,to=1.8,by=0.2) #rc=1

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F)

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F)

@@

```{r fig_verhulst, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()

pdf(paste(resloc,"verhulst_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

  ## Allow a second plot on the same graph
  par(new=TRUE)

  ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
       axes=FALSE, type="l", col="orange")
  abline(h=0,lty="dotted",col="grey")
  lines(s$d, s$pop_avg_acf_right, pch=16, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
  mtext("Avg. ACF",side=4,line=3.2,col="green4") 
  axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
}
par(op)
dev.off()
```

@@

pdf(paste(resloc,"verhulst_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025left,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=1,lty="dotted")

@@

rc_abrewer<-1/(K*(1-exp(-s*K)))

rlist<-sort(c(0.002,0.004,0.006,0.008,0.01,0.015,rc_abrewer,0.022,0.026))

>>>>

#Ricker model :
```{r sim_ricker, echo=F,  results="hide", cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

rc_ricker<-1 # transition from under to overcompensatory dynamics
r_bf_ricker<-2 # bifurcation parameter stable to unstable eqm

qrng<-runif(10000,min=0,max=r_bf_ricker)
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_ricker,length.out = 5),c(seq(from=rc_ricker,to=range(qr)[2],length.out = 5))))

numsims<-10000
numsteps<-25
numlocs<-5
K<-50
scl<-1
ext_thrs<-K/10
model<-"ricker"

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

```{r fig_ricker, echo=F, results="hide",cache=T, cache.extra=list(seed,res_ricker_local,res_ricker_global)}
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)

  #ylm2<-c(-0.2,0.6)
  ## Plot the second plot and put axis scale on right
  #plot(s$d, s$pop_avg_acf_left, pch=16,  xlab="", ylab="", ylim=ylm2,xlim=c(0,1),
       #ylim=range(-0.1,0.1), xlim=c(0,1),cex.axis=1.5,bty="n",
  #     axes=FALSE, type="l", col="orange")
 # abline(h=0,lty="dotted",col="grey")
 # lines(s$d, s$pop_avg_acf_right, col="skyblue")

  ## a little farther out (line=3.2) to make room for labels
 # mtext("Avg. ACF",side=4,line=3.2,col="green4") 
 # axis(4, ylim=ylm2, las=1,col="green4",col.axis="green4")
  #---------------------------------------------------------
}
par(op)
dev.off()

pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()
```

@@

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = c(0,2),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted") #rc=1

@@

numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
scl<-1
rc_hassell<-((b/(b-1)))^b # transition from under to overcompensatory dynamics
r_bf_hassell<- ((b/(b-2)))^b # bifurcation parameter stable to unstable eqm

qrng<-runif(10000,min=0,max=r_bf_hussell)
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_hassell,length.out = 5),c(seq(from=rc_hassell,to=range(qr)[2],length.out = 5))))

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

# For global dispersion
res_hassell_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

```{r fig_hassell, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()
```

@@

rc_msmith<-b/(b-1)
r_bf_msmith<-b/(b-2) # bifurcation parameter stable to unstable eqm

qrng<-runif(10000,min=0,max=r_bf_msmith)
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_msmith,length.out = 5),c(seq(from=rc_msmith,to=range(qr)[2],length.out = 5))))

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

# For global dispersal in D matrix 
res_msmith_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

```{r fig_msmith, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()

pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

```{r get_rc_pennycuick,echo=F,results="hide",cache=T,cache.extra=list(seed,mtime("1var_pop_model_bifurcation.R"))}
source("./1var_pop_model_bifurcation.R")
a_pennycuick<-0.1
b_pennycuick<-0.1
eps<-1e-10 #you can change it upto which decimal point you want it to be exact
rlist<-seq(from=4.3231657,to=4.3231659,by=eps)
res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r,a_pennycuick,b_pennycuick),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}

@@

rc_pennycuick<-rlist[which.min(abs(res_pennycuick-0))]
formatC(rc_pennycuick,digits = 10, format="f") # accurate upto 10th decimal

# This is to find the critical r value where stable to unstable eqm occurs
rlist<-seq(from=9.4672389,to=9.46724,by=eps)
#formatC(rlist,digits = 14, format="f")

res_pennycuick<-c() 
for(r in rlist){
  ans<-fn_d1_eqm(params=c(r=r,a_pennycuick,b_pennycuick),model="pennycuick")
  res_pennycuick<-c(res_pennycuick,ans)
}

#plot(rlist,res_pennycuick,col="red",type="l",xlab="r",ylab="pennycuick_1st_der_at_eqm")
#abline(h=0)
#fp<-0
fp<--1
r_bf_pennycuick<-rlist[which.min(abs(res_pennycuick-fp))]
#formatC(rc_pen_uns,digits = 14, format="f") 
```

```{r sim_pennycuick, echo=F,  results="hide", cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,r_bf_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

qrng<-runif(10000,min=0,max=r_bf_pennycuick)
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_pennycuick,length.out = 5),c(seq(from=rc_pennycuick,to=range(qr)[2],length.out = 5))))

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

# For global dispersal in D matrix 
res_pennycuick_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

```{r fig_pennycuick, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

rc_verhulst<-1 # transition from under to overcompensatory dynamics
r_bf_verhulst<-2 # bifurcation parameter stable to unstable eqm

qrng<-runif(10000,min=0,max=r_bf_verhulst)
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_verhulst,length.out = 5),c(seq(from=rc_verhulst,to=range(qr)[2],length.out = 5))))

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

@@

```{r fig_verhulst, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()

pdf(paste(resloc,"verhulst_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()
```

@@

pdf(paste(resloc,"verhulst_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025left,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted")

@@

rc_abrewer<-1/(K*(1-exp(-s*K))) # transition from under to overcompensatory dynamics
r_bf_abrewer<-2*rc_abrewer # bifurcation parameter stable to unstable eqm

qrng<-runif(10000,min=0,max=r_bf_abrewer)
qr<-quantile(qrng,probs=c(.025,.975))

rlist<-unique(c(seq(from=range(qr)[1],to=rc_abrewer,length.out = 5),c(seq(from=rc_abrewer,to=range(qr)[2],length.out = 5))))
